### 2014-05-20 tex/main-body-text.tex
Edited Fig2, made a greyscale version, and pointed to the GS version in the .tex

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1.jpg}  
    \caption{Assignment to reference population (from \textit{k} = 2-6) plots created 
in the program {\sc flock}. Each horizontal plot represents the 'best run' from a 
series where individuals are reallocated into \textit{k} clusters. Within each plot 
the normalized individual likelihood for each reference population is represented by a 
colored vertical bar. Major geographic boundaries that were attributed to genetic 
structure in \citet{Garzaetal_norcal} are indicated with black vertical lines. Results 
from the 'best runs' showed similar geographic differentiation to 
\citet{Garzaetal_norcal} analysis. The plateau analysis developed by 
\citet{Duc&Tur2012} indicate that either an undecided structure or that \textit{k}=2 
is the lower bound estimate.}
    \label{Fig.1}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
	% NOTE. Pat made Q-val-StrFloc.pdf that has all runs individually, replaced with 
	% all of them on same axis. It will look fine as a black and white with different 
	% characters.
 \includegraphics[width=\textwidth]{images/Figures-Pat/Qval-1plot.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1-GreyScale.pdf} % Flock-Fig1.jpg}  
    \caption{Assignment to reference population (from \textit{k} = 2-6) plots created 
in the program {\sc flock}. Each horizontal plot represents the 'best run' from a 
series where individuals are reallocated into \textit{k} clusters. Within each plot 
the normalized individual likelihood for each reference population is represented by a 
colored vertical bar. Major geographic boundaries that were attributed to genetic 
structure in \citet{Garzaetal_norcal} are indicated with black vertical lines. Results 
from the 'best runs' showed similar geographic differentiation to 
\citet{Garzaetal_norcal} analysis. The plateau analysis developed by 
\citet{Duc&Tur2012} indicate that either an undecided structure or that \textit{k}=2 
is the lower bound estimate.}
    \label{Fig.1}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
	% NOTE. Pat made Q-val-StrFloc.pdf that has all runs individually, replaced with 
	% all of them on same axis. It will look fine as a black and white with different 
	% characters.
 \includegraphics[width=\textwidth]{images/Figures-Pat/Qval-1plotGreyScale.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}
